---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# What quantitative and Qualitative Characteristics Affect Normalized-Loses of Automobiles?

## 1.0 Introduction

I found the raw data from:

- http://archive.ics.uci.edu/ml/datasets/Automobile

- https://www.kaggle.com/toramky/automobile-dataset

The producer of the raw data took this raw data from 1985 Ward's Automotive Yearbook.

The prdoducer of the raw data took from:

1. 1985 Model Import Car and Truck Specifications, 1985 Ward's Automotive Yearbook.
2. Personal Auto Manuals, Insurance Services Office, 160 Water Street, New York, NY 10038
3. Insurance Collision Report, Insurance Institute for Highway Safety, Watergate 600, Washington, DC 20037

## 2.0 Synopsis

I:

1. Loaded the csv file.
2. Found the percentage of NAs for the column 'normalized.losses'

## 3.0 Processing

Here's the code to find the percentage of NAs for the column 'normalised.loses'.
```{r Load}
#step 1 - load the file "automobile.data.csv" and "?" with NA using na.string

file_automobile<- read.csv("automobile.data.csv", na.strings = "?")

#step 2 - find the percentage of NAs for the column 'normalized.losses'

na_mean<-(mean(is.na(file_automobile$normalized.losses)))*100

#step 3 - find a subset of rows where in the column 'normalized.losses' is NA

na.normalised.loses<-file_automobile[is.na(file_automobile$normalized.losses),]
```

**`r na_mean`%** represents the percentage of missing or NAs for the column 'normalized.losses.'

Here's the code to find rows with NA values in the column 'normalized.losses' and plot a bar chart of the results.


## 4.0 Result

```{r pressure, echo=TRUE, fig.width=10}


#step - produce a bar chart showing make of cars which are NA for the column normalized.losses
par(mar=c(2,8,2,2))

barplot(-table(na.normalised.loses$make), horiz = TRUE, axes=FALSE, las=2, main = "Make of Cars which are NA for the column normalized.losses")
axis(1, at=-0:-8, labels=0:8)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
