---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# What quantitative and Qualitative Characteristics Affect Normalized-Loses of Automobiles?

## 1.0 Introduction

I found the raw data from:

- http://archive.ics.uci.edu/ml/datasets/Automobile

- https://www.kaggle.com/toramky/automobile-dataset

The producer of the raw data took this raw data from 1985 Ward's Automotive Yearbook.

The prdoducer of the raw data took from:

1. 1985 Model Import Car and Truck Specifications, 1985 Ward's Automotive Yearbook.
2. Personal Auto Manuals, Insurance Services Office, 160 Water Street, New York, NY 10038
3. Insurance Collision Report, Insurance Institute for Highway Safety, Watergate 600, Washington, DC 20037

## 2.0 Synopsis

I:

1. Loaded the csv file.
2. 

## 3.0 Processing

Here's the code
```{r Load}
#step 1 - create the working directory

#setwd("C:/Users/Elias/Desktop/cars/cars")

#file_car<- read.csv("car_evaluation.csv", header = FALSE, col.names = c('buying.price', 'maintaince.cost', 'number.doors', 'number.persons', 'lug.boot', 'safety', 'decision'))

#file_car[1:10]
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
